### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.1

\section{Implemented System}
The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts. First, the input files include the Roaming Agreement text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JSON file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.

@@

\section{Discussion of Results}
Since PDF, i.e., input files of the NLP Engine consist of unstructured text and e.g., undesired characters may remain despite parsing of the text, it is mandatory determine the \textit{accuracy} of the results obtained once the file with the classification of articles/sub-articles has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a verification based on human eye inspection and on the other hand, a verification based on symbol comparison. The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange. The experiments conducted to determine the accuracy are described below, while the results obtained are analyzed.

\subsection{Accuracy determination based on human eye inspection}
The first accuracy analysis involves randomly selecting 5 articles from each of the sample Roaming Agreements and performing a visual inspection (human-eye inspection) to determine the number of variables, variations, standard clauses and custom texts that exist. The results obtained are then compared with the values populated in the article and sub-article classification file for the same articles. Considering that the results obtained from the visual inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, the confusion matrices obtained are as follows:

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements. For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) has been used manually copying sub-article by sub-article. For each sub-article is determined:
 \begin{enumerate}
\item Common percentage of words between compared sub-articles.
\item Difference percentage of words between compared sub-articles.
\item Common words between compared sub-articles.
\item Difference words between compared sub-articles.
\end{enumerate}

Considering that for each sub-article the characters that determine the differences have been analyzed, determining that they are mostly end-of-line characters, quotation marks, parentheses and brackets, the threshold of the common percentage of words is determined as the worst case, i.e., where a greater combination of these characters appears. From the threshold, the rest of the cases found with lower common percentage of words will be considered failures.

>>>>

\section{Implemented System}
The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts. First, the input files include the Roaming Agreement text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.

@@

\section{Discussion of Results}
Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison. The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a variation, a standard clause or a customized text with respect to the GSMA standard template. Additionally, the detected variables are analyzed. The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles. Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text:
\begin{enumerate}
\item True Positive is when the item is observed and predicted.
\item True Negative is when the item is observed but not predicted.
\item False Positive is when the item is not observed but still predicted.
\item False Negative is when the item is neither observed nor predicted..
\end{enumerate}

The following confusion matrices allow us to analyze the results for each roaming agreement:

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements. For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) is used manually copying sub-article by sub-article. For each sub-article is determined:

 \begin{enumerate}
\item Common percentage of words between compared sub-articles.
\item Difference percentage of words between compared sub-articles.
\item Common words between compared sub-articles.
\item Difference words between compared sub-articles.
\end{enumerate}

The following radar plots allow us to analyze the results for each roaming agreement:
